---
title: "S-Class Analysis"
author: "Varun Venkatesh"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE,echo=FALSE}
library(tidyverse)
library(boot)
library(knitr)

df <- read.csv("sclass.csv")
```

## Part A: Bootstrap Confidence Interval for Average Mileage

### Claim
Estimate a 95% bootstrap confidence interval for the average mileage of 2011 S-Class 63 AMG vehicles.

### Evidence
```{r,echo=FALSE}
# Filter data for year 2011 and trim "63 AMG"
df_2011_63AMG <- df %>% filter(year == 2011, trim == "63 AMG")

# Check summary statistics
summary(df_2011_63AMG$mileage)

# Bootstrap function
df_boot <- function(data, indices) {
  sample_data <- data[indices, ]
  return(mean(sample_data$mileage, na.rm = TRUE))
}

# Perform bootstrap
set.seed(123)
boot_results <- boot(df_2011_63AMG, df_boot, R = 1000)
ci_95 <- boot.ci(boot_results, type = "perc")
kable(data.frame(Lower = ci_95$percent[4], Upper = ci_95$percent[5]))
```

### Conclusion
The 95% bootstrap confidence interval for the average mileage of 2011 S-Class 63 AMG vehicles is derived through repeated resampling. This interval offers a reliable estimate of the true mean mileage


## Part B: Bootstrap Confidence Interval for Proportion of Black Cars

### Claim
Estimate a 95% bootstrap confidence interval for the proportion of 2014 S-Class 550 vehicles that were painted black.

### Evidence
```{r,echo=FALSE}
# Filter data for year 2014 and trim "550"
df_2014_550 <- df %>% filter(year == 2014, trim == "550") %>% mutate(isBlack = ifelse(color == "Black", TRUE, FALSE))

# Check proportions
prop_black <- mean(df_2014_550$isBlack, na.rm = TRUE)
kable(data.frame(Proportion_Black = prop_black))

# Bootstrap function
df_boot_prop <- function(data, indices) {
  sample_data <- data[indices, ]
  return(mean(sample_data$isBlack, na.rm = TRUE))
}

# Perform bootstrap
set.seed(123)
boot_results_prop <- boot(df_2014_550, df_boot_prop, R = 1000)
ci_95_prop <- boot.ci(boot_results_prop, type = "perc")
kable(data.frame(Lower = ci_95_prop$percent[4], Upper = ci_95_prop$percent[5]))
```

### Conclusion
The 95% bootstrap confidence interval for the proportion of 2014 S-Class 550 vehicles that were black is based on repeated sampling. This interval provides a reliable estimate of the true proportion, showing that a significant number of these cars were black. This trend makes sense, as luxury vehicles are often painted in darker colors for their sleek look and strong resale value.
