---
title: "NBC Pilot Survey Analysis"
author: "Varun Venkatesh"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE,echo=FALSE}
library(tidyverse)
library(broom)
library(knitr)
library(boot)

df <- read.csv("nbc_pilotsurvey.csv")
```

## Part A: Happiness Comparison Between "Living with Ed" and "My Name is Earl"

### Question
Who makes people happier: Ed or Earl?

### Approach
A 95% confidence interval for the difference in mean Q1_Happy scores between "Living with Ed" and "My Name is Earl" was calculated.

### Results
```{r,echo=FALSE}
# Filter data
df_happy <- df %>% filter(Show %in% c("Living with Ed", "My Name is Earl"))

# T-test for mean difference
happy_ttest <- t.test(Q1_Happy ~ Show, data = df_happy)
kable(tidy(happy_ttest))
```

### Conclusion
The confidence interval for the mean difference shows whether one show tends to make viewers happier than the other. If the interval doesn’t include zero, it suggests a meaningful difference in happiness ratings.

## Part B: Annoyance Comparison Between "The Biggest Loser" and "The Apprentice: Los Angeles"

### Question
Which reality/contest show made people feel more annoyed?

### Approach
A 95% confidence interval for the difference in mean Q1_Annoyed scores between "The Biggest Loser" and "The Apprentice: Los Angeles" was computed.

### Results
```{r,echo=FALSE}
# Filter data
df_annoyed <- df %>% filter(Show %in% c("The Biggest Loser", "The Apprentice: Los Angeles"))

# T-test for mean difference
annoyed_ttest <- t.test(Q1_Annoyed ~ Show, data = df_annoyed)
kable(tidy(annoyed_ttest))
```

### Conclusion
The confidence interval helps determine whether one show is consistently more annoying than the other. If zero is not within the interval, it indicates a significant difference in annoyance levels.

## Part C: Confusion Proportion for "Dancing with the Stars"

### Question
What proportion of viewers found "Dancing with the Stars" confusing?

### Approach
A 95% confidence interval for the proportion of viewers who rated "Q2_Confusing" as 4 or 5 was computed.

### Results
```{r,echo=FALSE}
# Filter data
df_confused <- df %>% filter(Show == "Dancing with the Stars") %>% mutate(isConfused = Q2_Confusing >= 4)

# Compute proportion
confusion_prop <- mean(df_confused$isConfused, na.rm = TRUE)

# Bootstrap function
prop_boot <- function(data, indices) {
  sample_data <- data[indices, ]
  return(mean(sample_data$isConfused, na.rm = TRUE))
}

# Perform bootstrap
set.seed(123)
boot_results_conf <- boot(df_confused, prop_boot, R = 1000)
ci_95_conf <- boot.ci(boot_results_conf, type = "perc")
kable(data.frame(Lower = ci_95_conf$percent[4], Upper = ci_95_conf$percent[5]))
```

### Conclusion
The confidence interval gives an estimate of how many American viewers found Dancing with the Stars confusing. This analysis sheds light on how audiences perceive a show that seems straightforward.
