---
title: "EBay Paid Search Advertising Analysis"
author: "Varun Venkatesh"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE,echo=FALSE}
library(tidyverse)
library(boot)
library(knitr)

df <- read.csv("ebay.csv")
```

## Question
Does turning off paid search advertising on Google affect EBay’s revenue?

## Approach
We compute the **revenue ratio** (rev_after / rev_before) for each DMA and compare the mean revenue ratio between treatment (adwords_pause = 1) and control (adwords_pause = 0) groups. A **95% confidence interval** for the difference in means is estimated using **bootstrap resampling with 10,000 simulations**.

## Results
```{r,echo=FALSE}
# Compute revenue ratio
df <- df %>% mutate(revenue_ratio = rev_after / rev_before)

# Split data into treatment and control
treatment <- df %>% filter(adwords_pause == 1) %>% pull(revenue_ratio)
control <- df %>% filter(adwords_pause == 0) %>% pull(revenue_ratio)

# Bootstrap function
boot_diff <- function(data, indices) {
  sample_data <- data[indices, ]
  return(mean(sample_data$treatment) - mean(sample_data$control))
}

# Create bootstrapped differences
set.seed(123)
boot_data <- data.frame(treatment = sample(treatment, 10000, replace = TRUE),
                        control = sample(control, 10000, replace = TRUE))

# Compute confidence interval
ci_95 <- quantile(boot_data$treatment - boot_data$control, probs = c(0.025, 0.975))
kable(data.frame(Lower = ci_95[1], Upper = ci_95[2]))
```

## Conclusion
The 95% confidence interval estimates the **true effect of pausing paid search** on revenue. If the confidence interval contains zero, there is **no evidence** that paid search significantly impacts revenue. If the interval is negative, it suggests that **pausing paid search reduces revenue**. This analysis informs whether paid search ads justify their cost.
